---
title: "Peer-graded Assignment: Course Project: Shiny Application and Reproducible Pitch"
author: "N Vinod Kumar"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
This application is a Restaurant Dashboard, which allows the users to View the various Menu categories and Menu Items of a Restaurant. The users can be able to see the no of categories and Menu Items available under a selected category.

## UI

- Slider Input - For selecting the Price
- Select Input - for selecting the Menu Categories

There are 3 tabs in the Application
1. Table
2. Plot
3. Help

## Resturant Data Set Used for this Project

```{r cars, echo = TRUE}
load(file = "resturantdata.rda")
summary(resturantdata)
library(dplyr)
library(plotly)
```

## Slide with Plot

```{r pressure, echo = FALSE}
categorydata <- resturantdata %>% group_by(MenuCategory) %>% summarise(Items = n())
        plot_ly(categorydata, x = ~MenuCategory, y = ~Items, type = 'bar', color=~MenuCategory) %>% layout(barmode="overlay",
                    title = "Menu Category",                                       
                       xaxis = list(title = "Menu Category", tickangle = 90),
                   yaxis = list(title = "No. of Items available"))
```

## Thanks